---
title: "The PD SRM in R"
output: pdf_document
author: Lara Stas
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# The standard PD SRM
## Step 1: Read in your data.

Suppose you want to use a datafile called \texttt{data} which is located in the folder \texttt{datafolder}.

```{r, message = F, echo = FALSE}
# Read in your data -------
  # Step 1a: Specify the path to your data
    setwd("H:/home/Doctoraat/Studie 3 - PD SRM/Data/finale data/per item")
      # to do: change to my documents before submission.
  # Step 1b: read in your data (only run the relevant line)
      # for txt-files:
        mydata <- read.table("CA_eat_1ind.txt")
      # for csv-files
```

```{r, message = F, eval = F}
# Read in your data -------
  # Step 1a: Specify the path to your data
    setwd("C:\Users\laras\Documents\datafolder")
  # Step 1b: read in your data (only run line with the correct extension of your file)
      # for txt-files:
        mydata <- read.table("data.txt")
      # for csv-files
        mydata <- read.csv("data.csv")
      # for SPSS-files
        library(foreign)
        mydata <- read.spss("data.sav")
```

```{r, message = F, echo = FALSE}
  # Step 1c: take a look at the first lines of your data file
        head(mydata[,-1])
```

```{r, message = F, eval = F}
  # Step 1c: take a look at the first lines of your data file
        head(mydata)
```

On top of the collumns, the variable names are displayed. Note that the variables in this data set are labelled as MF, MO, MY, FO, FY and YO. Here, \texttt{M} represents mother, \texttt{F} father, \texttt{Y} youngest child and \texttt{O} oldest child. 
These variable names are used in step 2.

## Step 2: Specify the Purely Dyadic Social Relations Model.
Note that the following operators are used by lavaan for specifying your model:
\begin{itemize}
  \item  To specify the indicators (i.e., observed items) of each latent variable (i.e., PD SRM components) the operator =\textasciitilde  is used. This operateor can be read as \textit{is manifested by}
  \item To specify (residual) variances and covariances in the model syntax: \textasciitilde\textasciitilde
  \item For defining intercepts: \textasciitilde \texttt{label*1}
  \item == means \textit{is equal to}
  \item > means \textit{is larger than}
\end{itemize}

```{r, message = F}
PDSRM <- '
  # Specify the indicators for each PD SRM component (cfr. Figure 3)
  # If you use other names for your variables, please adapt this in the following script
  FC =~ lambdaMF*MF + lambdaMO*MO + lambdaMY*MY + lambdaFO*FO + lambdaFY*FY + lambdaYO*YO
  I.M =~ 1*MF + 1*MO + 1*MY
  I.F =~ 1*MF + 1*FO + 1*FY 
  I.O =~ 1*MO  + 1*FO + 1*YO
  I.Y =~ 1*MY  + 1*FY + 1*YO
  D.MF =~ 1*MF
  D.MO =~ 1*MO
  D.MY =~ 1*MY
  D.FO =~ 1*FO
  D.FY =~ 1*FY
  D.OY =~ 1*YO
  
  # Variances
  FC ~~ VAR.FC*FC
  I.M ~~ VAR.I.M*I.M
  I.F ~~ VAR.I.F*I.F
  I.O ~~ VAR.I.O*I.O
  I.Y ~~ VAR.I.Y*I.Y
  D.MF ~~ VAR.D.MF*D.MF
  D.MO ~~ VAR.D.MO*D.MO
  D.MY ~~ VAR.D.MY*D.MY
  D.FO ~~ VAR.D.FO*D.FO
  D.FY ~~ VAR.D.FY*D.FY
  D.OY ~~ VAR.D.OY*D.OY
  
  # Means
  FC ~ mean.FC*1
  I.M ~ mean.I.M*1
  I.F ~ mean.I.F*1
  I.O ~ mean.I.O*1
  I.Y ~ mean.I.Y*1
  D.MF ~ mean.D.MF*1
  D.MO ~ mean.D.MO*1
  D.MY ~ mean.D.MY*1
  D.FO ~ mean.D.FO*1
  D.FY ~ mean.D.FY*1
  D.OY ~ mean.D.OY*1

  # Constraints
  mean.I.M + mean.I.F +  mean.I.O + mean.I.Y == 0
  mean.D.MF + mean.D.MO + mean.D.MY == 0
  mean.D.MF + mean.D.FO +  mean.D.FY == 0
  mean.D.MY + mean.D.FY + mean.D.OY == 0
  mean.D.MO + mean.D.FO + mean.D.OY == 0
  
  # set constraints on factor loadings FC for identifiability
  lambdaMF + lambdaMO + lambdaMY + lambdaFO + lambdaFY + lambdaYO == 6

  # No negative variances are allowed (cfr. other software like EQS)
  VAR.FC  > 0
  VAR.I.M > 0
  VAR.I.F > 0
  VAR.I.O > 0
  VAR.I.Y > 0
  VAR.D.MF > 0
  VAR.D.MO > 0
  VAR.D.MY > 0
  VAR.D.FO > 0
  VAR.D.FY > 0
  VAR.D.OY > 0
'
```

If you are interested in calculating intragenerational similarities these can be requested by adding the following lines to the previous syntax:
```{r, message = F, eval = F}
I.M ~~ I.F
I.O ~~ I.Y
```

Note that when running this adapted model, you will have 3 (instead of 5) degrees of freedom left. 

## Step 3: Fit the model with your data and request the output
If you are using R for the first time on this device, please make sure to install the \texttt{lavaan} package first by running \texttt{install.packages("lavaan")}.


```{r, message = F}
# load the lavaan package
  library(lavaan)
# fit the model with the data and ask a summary of the results
  fit <- lavaan(model = PDSRM, data = mydata, missing = "fiml")
  summary(fit, fit.measures = T)
```


# Extending the Standard PD SRM
The standard PD SRM can be extended to investigate more complex research questions as well. This can easily be done by adding one line of code to the model. We will discuss two plausible extensions. First, one might want to test an hypotheses that involves the direct comparison of two PD SRM components. For example, for testing if mothers share more family meals with all family members than fathers do a new parameter can be defined. This is done by subtracting the two relevant components and checking if this new parameter differs significantly from zero (i.e., diff = mean.I.M - mean.I.F). 
```{r, message = F}
PDSRM3 <- paste0(PDSRM, 'diff := mean.I.M - mean.I.F' )
fit3 <- lavaan(model = PDSRM3, data = mydata, missing = "fiml")
summary(fit3, fit.measures = T)
```
No significant difference between the amount of meals mothers and father share with all family members is found (diff = 0.251, p = 0.741). 

Do mothers and fathers differ in the unique coordination they have with their children? 

```{r, message = F}
PDSRM4 <- paste0(PDSRM, 'diffO := mean.D.MO - mean.D.FO
                 diffY := mean.D.MY - mean.D.FY' )
fit4 <- lavaan(model = PDSRM4, data = mydata, missing = "fiml")
summary(fit4, fit.measures = T)
```


Second, a researcher might be interested in testing additional correlations between two PD SRM components. This can be done by placing a double tilde (i.e., \textasciitilde\textasciitilde) between the two components of interest. For example, if one aims to investigate if it is true that the more meals the youngest child shares with the mother, the more these children also tend to share with the father, one can allow a correlation between the mother-youngest child dyadic component and the father-youngest child dyadic component (e.g., D.MY \textasciitilde\textasciitilde D.FY).


```{r, message = F}
PDSRM2 <- paste0(PDSRM, 'D.MY ~~ D.FY' )
fit2 <- lavaan(model = PDSRM2, data = mydata, missing = "fiml")
summary(fit2, fit.measures = T)
```
As can be seen in the output, this correlation is not significant.


# The PD SRM with two indicators

Now suppose you have a data set called \texttt{mydata2ind.txt.}
```{r, message = F, echo = FALSE}
 # read in data
        setwd("H:/home/Doctoraat/Studie 3 - PD SRM/Data/finale data/per item")
        mydata2ind <- read.table("simdata2ind.txt")
```

```{r, message = F, eval = FALSE}
 # read in your data
      mydata2ind <- read.table("mydata2ind.txt")
```
```{r, message = F}
 # The PD SRM with 2 indicators
 PDSRM_2ind <- '
      # Latent variables
      FC =~ lambdaMF1*MF1 + lambdaMO1*MO1 + lambdaMY1*MY1 + lambdaFO1*FO1 + lambdaFY1*FY1 + 
            lambdaYO1*YO1 + lambdaMF2*MF2 + lambdaMO2*MO2 + lambdaMY2*MY2 + lambdaFO2*FO2 + 
            lambdaFY2*FY2 + lambdaYO2*YO2
      I.M =~  1*MF1 + 1*MO1 + 1*MY1 +
              1*MF2 + 1*MO2 + 1*MY2  
      I.F =~  1*MF1 + 1*FO1 + 1*FY1 +
              1*MF2 + 1*FO2 + 1*FY2 
      I.O =~  1*MO1  + 1*FO1 + 1*YO1 +
              1*MO2  + 1*FO2 + 1*YO2
      I.Y =~  1*MY1  + 1*FY1 + 1*YO1 +
              1*MY2  + 1*FY2 + 1*YO2
      D.MF =~ 1*MF1 + 1*MF2
      D.MO =~ 1*MO1 + 1*MO2
      D.MY =~ 1*MY1 + 1*MY2
      D.FO =~ 1*FO1 + 1*FO2
      D.FY =~ 1*FY1 + 1*FY2
      D.OY =~ 1*YO1 + 1*YO2
      
      # Variances
      FC ~~ VAR.FC*FC
      I.M ~~ VAR.I.M*I.M
      I.F ~~ VAR.I.F*I.F
      I.O ~~ VAR.I.O*I.O
      I.Y ~~ VAR.I.Y*I.Y
      D.MF ~~ VAR.D.MF*D.MF
      D.MO ~~ VAR.D.MO*D.MO
      D.MY ~~ VAR.D.MY*D.MY
      D.FO ~~ VAR.D.FO*D.FO
      D.FY ~~ VAR.D.FY*D.FY
      D.OY ~~ VAR.D.OY*D.OY
      MF1 ~~ MF1
      MO1 ~~ MO1 
      MY1 ~~ MY1
      FO1 ~~ FO1
      FY1 ~~ FY1
      YO1 ~~ YO1
      MF2 ~~ MF2
      MO2 ~~ MO2 
      MY2 ~~ MY2
      FO2 ~~ FO2
      FY2 ~~ FY2
      YO2 ~~ YO2
      
      # Intercepts
      FC ~ mean.FC*1
      I.M ~ mean.I.M*1
      I.F ~ mean.I.F*1
      I.O ~ mean.I.O*1
      I.Y ~ mean.I.Y*1
      D.MF ~ mean.D.MF*1
      D.MO ~ mean.D.MO*1
      D.MY ~ mean.D.MY*1
      D.FO ~ mean.D.FO*1
      D.FY ~ mean.D.FY*1
      D.OY ~ mean.D.OY*1
      
      # intragenerational similarity
      # I.M ~~ I.F
      # I.O ~~ I.Y
      
      # Constraints
      mean.I.M + mean.I.F +  mean.I.O + mean.I.Y == 0
      mean.D.MF + mean.D.MO + mean.D.MY == 0
      mean.D.MF + mean.D.FO +  mean.D.FY == 0
      mean.D.MY + mean.D.FY + mean.D.OY == 0
      mean.D.MO + mean.D.FO + mean.D.OY == 0

      # no negative variances are allowed (cfr. other software)
      VAR.FC  > 0
      VAR.I.M > 0
      VAR.I.F > 0
      VAR.I.O > 0
      VAR.I.Y > 0
      VAR.D.MF > 0
      VAR.D.MO > 0
      VAR.D.MY > 0
      VAR.D.FO > 0
      VAR.D.FY > 0
      VAR.D.OY > 0
      
      # set constraints on factor loadings FE for identifiability
      12 == lambdaMF1 + lambdaMO1 + lambdaMY1 + lambdaFO1 + lambdaFY1 + lambdaYO1 + 
            lambdaMF2 + lambdaMO2 + lambdaMY2 + lambdaFO2 + lambdaFY2 + lambdaYO2 
      '

    # fit the model with your data and request a summary
    fit_2ind <- lavaan(data = mydata2ind, model = PDSRM_2ind)
    summary(fit_2ind, fit.measures = T)  
```
