---
title: "R Code for Calculating the Relative Importance of Each Component in a PD Observed Score"
output: pdf_document
author: Lara Stas
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First, read in the following function by running the following lines. 

```{r, message = F}
# function for calculating amount of relative variance (no need to modify)
relvar <- function(c1, c2, c3, c4){
  tot <- c1+c2+c3+c4
  rv1 <- round(c1/tot*100,2)
  rv2 <- round(c2/tot*100,2)
  rv3 <- round(c3/tot*100,2)
  rv4 <- round(c4/tot*100,2)
  cat("% of variance explained by", deparse(substitute(c1)), " = ",rv1, 
      "\n% of variance explained by", deparse(substitute(c2)), " = ",rv2, 
      "\n% of variance explained by", deparse(substitute(c3)), " = ",rv3, 
      "\n% of variance explained by", deparse(substitute(c4)), " = ",rv4)
}
```

Now, this function can be used to calculate the relative importance of each PD SRM component in a purely dyadic (observed) score.
First, specify the estimated variance of each component (you can find this in the lavaan output under the header "Variances")

Legend: 
\begin{itemize}
  \item fam = family component
  \item i =  individual component
  \item d = dyadic component
  \item roles: mo = mother; fa = father; oc = oldest child; yc = youngest child.
\end{itemize}

```{r, message = F}
# Estimated variance of each component
  fam <- 0.473
  i.mo <- 0.129
  i.fa <- 0.417
  i.oc <- 0.099
  i.yc <- 0
  d.mofa <- 0.261
  d.mooc <- 0.168
  d.moyc <- 0.063
  d.faoc <- 0.045
  d.fayc <- 0.094
  d.ycoc <- 0.473
```

Than, tell R by which components the PD scores are defined. For example, as can be seen in Figure 3 of the manuscript, the PD score of the mother-father dyad is a function of the family component, the individual component of the mother, the individual component of the father and the mother-father dyadic component.

```{r, message = F}
# mother-father PD score
  relvar(c1 = fam, c2 = i.mo, c3 = i.fa, c4 = d.mofa)
# mother-oldest child PD score
  relvar(c1 = fam, c2 = i.mo, c3 = i.oc, c4 = d.mooc)
# mother-youngest child PD score
  relvar(c1 = fam, c2 = i.mo, c3 = i.yc, c4 = d.moyc)
# father-oldest child PD score
  relvar(c1 = fam, c2 = i.fa, c3 = i.oc, c4 = d.faoc)
# father-youngest child PD score
  relvar(c1 = fam, c2 = i.fa, c3 = i.yc, c4 = d.fayc)
# youngest-oldest child PD score
  relvar(c1 = fam, c2 = i.yc, c3 = i.oc, c4 = d.ycoc)
```
